Sequential rank agreement methods for comparison of ranked lists

### 2016-05-20 latex/superranker-manuscript.tex
closing in on asymptotic

\documentclass[12pt,a4paper]{article}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
%\usepackage{geometry}
%\geometry{a4paper, portrait, margin=1in}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\arginf}{arginf}

@@

Consider a set of $P$ different items $X=\{X_1,\dots,X_P\}$ and a
ranking function $R: \{X_1,\dots,X_P\}\to \{1,\dots,P\}$, such that
$R(X_p)$ is the rank of item $X_p$. The inverse mapping $R^{-1}$ gives
the item $R^{-1}(r)$ that was assigned to rank $r\in\{1,\dots,P\}$. An
ordered list is the realization of a ranking function $R$ applied to
the set of items $X$. In all what follows we condition on the set of
items and consider the ranking function to be a random variable. Thus,
let $R_1(X),\dots,R_L(X)$, $L\geq2$, be a sample of $L$ independent
identically distributed draws from an unknown probability distribution
function $Q$. One aim is then to test how much $Q$ resembles the
uniform distribution which assigns probability $(1/P)^P$ to each of
the $P^P$ different rankings.

@@

Panels (a) and (b) of
Table~\ref{tab:example} show a schematic example of these
mappings. Thus if $R_l^{-1}(1)=X_{34}$ then item $X_{34}$ is ranked
first in list $l$ and similarly $R_l(X_{34})=1$.

@@

The agreement of the lists regarding the rank given to an item $X_p$
can be measured by the expected variance across the lists:
\begin{equation}
  {A}(X_p) = \sum_{r=1}^{P^P} \{r(X_P)-\E_Q R(X_P)\}^2 Q(r)
\end{equation}
where $\E_Q R(X_p)=\sum_{r=1}^{P^P} r(X_p)Q(r)$. The empirical
counterpart is

\begin{align}
\widehat{A}_L(X_p) = \frac{1}{L-1}\sum_{i=1}^L (R_i(X_p) - \overline{R}(X_p))^2, \quad \overline{R}_L(X_p) = \frac{1}{L}\sum_{i=1}^L R_i(X_p).
\end{align}
For each item, the function $\widehat{A}_L$ has an interpretation as the expected
Euclidean distance of the individual rankings from the expected
ranking over the $L$ lists, and it corresponds to the same measure
that is used in method comparison studies to compute the limits of
agreement \citep{alt:bland:1983}.

\bigskip\hrule HOV
Vi kunne sige her: Alternative distance functions (f non-negativ real valued) are discussed in section ??
\hrule\bigskip 
% \begin{equation}
  % \widehat{A_L}(X_p) = f(R_1(X_p), \ldots, R_L(X_p))
% \end{equation}
% for a measurable non-negative real-valued distance function $f$.
For an integer $1\le d\le P$ we define the expected set of unique
items found by merging the first $d$ elements across the possible
lists:
\begin{equation}
S_d = \{X_p; \left(\sum_{r=1}^{P^P} I\{r(X_p)\le d\} Q(r)\right) >0\}.
\end{equation}
The empirical counterpart the set of unique items ranked less than or
equal to $d$ in any of the $L$ lists:
\begin{equation}
\widehat{S}_{d,L} = \{X_p; \left(\sum_{l=1}^L I\{R_l(X_p)\le d\}\right)>0\},
\end{equation}
which is exemplified in Panel (c) of Table \ref{tab:example}.

We then define the \emph{sequential rank agreement} as the weighted
expected agreement of the items found in the set $S_d$:
\begin{equation}
  \textrm{sra}(d) = \frac{\sum_{\{p \in S_d\}}A(X_p)}{|S_d|}\label{def:sra}
  % & =\sum_{p=1}^P \sum_{l=1}^L I\{R_l(X_p)\le d\}>0\}\notag
\end{equation}
 where $|S_d|$ is the cardinality of the set $S_d$.
The empirical counterpart is given by
\begin{equation}
  \widehat{\textrm{sra}}_L(d) = \frac{\sum_{\{p \in \widehat{S}_{d,L}\}}(L-1)\widehat{A_L}(X_p)}{(L-1)|\widehat {S}_{d,L}|}.\label{def:sra}
                                % \intertext{where}
                                % |S_d| & =\sum_{p=1}^P \sum_{l=1}^L I\{R_l(X_p)\le d\}>0\}\notag
\end{equation}
% where is the cardinality of the set $\widehat{S}_{d,L}$.

Values of \textrm{sra} close to zero suggests that the lists agree
while larger values suggest disagreement.

Just like in method comparison studies we prefer smaller limits of
agreement because that means that the differences between the methods
is small. If the ranked lists are identical then the value of
sequential rank agreement will be zero for all depths $d$.
%Note that the terms that are part of \eqref{def:sra} are not
%independent since every list contains the ranks from 1 to $P$ exactly
%once. As a consequence we simply use the pooled standard deviation as
%a measure of the average distance between rankings and we refrain from
%using traditional distributional results for this measure.

The sequential rank agreement then becomes equivalent to the pooled
variance of the items found in $S_d$, and it can be interpreted as the
average distance of the individual rankings of the lists from the
average ranking for each of the items we have seen until depth $d$.

\subsection{Population parameter}

Given a sample of $1,\ldots,L$ lists an estimator of the sequential
rank agreement is given by
\begin{equation}
\widehat{\textrm{sra}}_L(d)= \frac{\sum_{\{p \in S_d\}}(L-1)\widehat{A_L}(X_p)}{(L-1)|S_d|}\label{def:sra}
\end{equation}
where
\begin{align}
\widehat{A}_L(X_p) = \frac{1}{L-1}\sum_{i=1}^L (R_i(X_p) - \overline{R}(X_p))^2, \quad \overline{R}_L(X_p) = \frac{1}{L}\sum_{i=1}^L R_i(X_p)
\end{align}
is the sample variance of the rank of item $X_p$. For an easier interpretation we suggest to plot $\widehat{\textrm{sra}}_L(d)^{1/2}$ corresponding to the pooled standard deviation. The consistency of $\widehat{\textrm{sra}}_L$ as $L \rightarrow \infty$ will be discussed further in section \ref{sec:chgpoint}.

@@

With fully observed lists we can plot the sequential rank agreement
\eqref{def:sra} as a function of depth $d$. An example is seen in top
panels of Figure~\ref{fig:example1} where four analysis methods were
used to rank 3051 gene expression values measured on 38 tumor mRNA
samples in order to classify between acute lymphoblastic leukemia
(ALL) and acute myeloid leukemia (AML)
\citep{Golub1999}. Preprocessing of the gene expression data was done
as described in \citet{Dudoit2002} and the four different analysis
approaches were: marginal two-sample $t$ tests, marginal logistic
regression analyses, elastic net logistic regression
\citep{friedman2010regularization}, and marginal maximum information
content correlations (MIC) \citep{Reshef2011}. For the first two
methods, the genes were ranked according to minimum $p$ value, for
logistic regression the genes were ordered by size of the
corresponding coefficients (after standardization), and MIC was
ordered by absolute correlation which resulted in the top rankings
seen in Table~\ref{tab1}.

@@

\section{Evaluating sequential rank agreement}

To interpret the sequential rank agreement values we propose two
different benchmark values corresponding to two different
hypotheses. We wish to determine if we observe better agreement than
what would be expected if there were no relevant information available
in the data.

@@

\section{Change-point analysis}\label{sec:chgpoint}
In many applications it is of interest to estimate a list depths which
satisfies a change point criterion. In this section we investigate the
theoretical properties of our proposed method for this specific
task. As Hall and Schimek, we work with an infinite set of lists
$\mathcal{L}$ and study the asymptotic behaviour for $L\to\infty$.
%However, we do not allow the length of the lists to
%change with $L$ as in most applications the length of the lists is
%fixed [FIXME: for finite $L$ are there only finitely many forskelige
%lists (aber dass stoert keinen grossen geist, siger karlsson)].
First, we define the parameter of interest. For any given threshold value $q$
a change-point $d^\ast(q)$ in the list agreement is defined by
\begin{equation}
  d^\ast(q) = \arginf_{d\in\{1,\dots,P\}}\textrm{sra}(d)>q.
\end{equation}
The value of $q$ could for example be the agreement of randomly
permuted lists [FIXME: there is only one SRA value for infinitely many
random permutations, no skygge!].
The corresponding estimated change-point is similarly defined by
\begin{equation}
\widehat{d^\ast_L}(q) = \arginf_{d\in\{1,\dots,P\}}\widehat{\textrm{sra}}_L(d)>q
\end{equation}

We start by showing that $\widehat{\textrm{sra}}_L$ is consistent for $\textrm{sra}$ for $P,L \rightarrow \infty$ and $\frac{P}{L} \rightarrow 0$.
The consistency of $\widehat{d^\ast_L}(q)$ then follows by a simple corollary. The proof requires the following assumptions.

\begin{assumption}
We assume that:
\begin{enumerate}[label=\Alph*)]
\item{hej}
\item{med}
\item{dig}
\end{enumerate}
\end{assumption}

\begin{theorem}
Under the assumptions it follows that $\widehat{\textrm{sra}}_L \overset{P}{\longrightarrow} \textrm{sra}$ for $L,P\rightarrow \infty$ and $\frac{P}{L} \rightarrow 0$.
\begin{proof}
We start by noting that we can rewrite the sequential rank agreement in equation \ref{def:sra} as
\begin{align}
\textrm{sra}(d) &= \frac 1{\sum_{p=1}^P \sum_{l=1}^L 1\{R_l(X_p)\le d\}}\sum_{p=1}^P(1-\prod_{l=1}^L 1\{R_l(X_p)>d\}) \E[A(X_p)]\\
    &= \frac{1}{L} \sum_{l=1}^L \sum_{p=1}^P S_l(p)
\end{align}
where
\begin{align}
  S_l(p) &= ?
\end{align}
Maybe we can use the LLN for triangular arrays?
\end{proof}
\label{thm:consistency}
\end{theorem}

\begin{corollary}
For fixed $q$ it follows from theorem \ref{thm:consistency} that
$\widehat{d^\ast_L}(q) \overset{P}{\longrightarrow} d^\ast(q)$
for $L \rightarrow \infty$.
\begin{proof}
 hej
\end{proof}
\end{corollary}

\section{Comparison to average overlap}

The average overlap is a measure that is widely used in comparisons of
two fully observed ranked lists \citep{Fagin2003,Webber2010} and the
idea behind the average overlap closely resembles the sequential rank
agreement. In this section we present an extension of the average
overlap to more that two lists and compare this to sequential rank
agreement.

The overlap among $L$ lists observed until depth $d$ is defined as the
proportion of items that are found in all $L$ lists compared to the
possible number of items found in all lists observed until depth $d$:
\begin{equation}
  O(d) = \frac{| \cap_{l=1}^L \{R_l^{-1}(r); r\leq d \} |}{d}\label{def:overlap}
\end{equation}
Typically the overlap is only considered for pairwise comparisons
\citep{Bar-Ilan2006,Boulesteix2009} but formula \ref{def:overlap}
is easily extended to the situation where $L>2$ as shown above.

@@

>>>>

\documentclass[12pt,a4paper]{article}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{color}
\usepackage{subcaption}
\usepackage{natbib}
\usepackage{xspace}
\usepackage{calc}
%\usepackage[noae]{Sweave}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
%\usepackage{geometry}
%\geometry{a4paper, portrait, margin=1in}
%
% New commands
%
\newcommand{\ie}{\emph{i.e.}\@\xspace}
\newcommand{\eg}{\emph{e.g.}\@\xspace}

\newcommand{\nn}{\nonumber}

\newcommand{\mcomment}[1]{\textcolor{red}{\textbf{#1}}}

\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\Cov}{Cov}
\newcommand{\argmin}{\operatornamewithlimits{arg\,min}}

@@

Consider a set of $P$ different items $X=\{X_1,\dots,X_P\}$ and a
ranking function $R: \{X_1,\dots,X_P\}\to \{1,\dots,P\}$, such that
$R(X_p)$ is the rank of item $X_p$. The inverse mapping $R^{-1}$ gives
the item $R^{-1}(r)$ that was assigned to rank $r\in\{1,\dots,P\}$. An
ordered list is the realization of a ranking function $R$ applied to
the set of items $X$. In all what follows we condition on the set of
items and consider the ranking function to be a random variable. Thus,
let $R_1(X),\dots,R_L(X)$, $L\geq2$, be a sample of $L$ independent
identically distributed draws from an unknown probability distribution
function $Q$. One aim is then to test how much $Q$ resembles the
uniform distribution which assigns probability $(P!)^{-1}$ to each of
the $P!$ different rankings.
Panels (a) and (b) of
Table~\ref{tab:example} show a schematic example of these
mappings. Thus if $R_l^{-1}(1)=X_{34}$ then item $X_{34}$ is ranked
first in list $l$ and similarly $R_l(X_{34})=1$.

@@

@@

The agreement of the lists regarding the rank given to an item $X_p$
can be measured by the variance across the lists
\begin{equation}
  {A}(X_p) = \sum_{r=1}^{P!} \{r(X_P)-\E_Q R(X_P)\}^2 Q(r)
\end{equation}
where $\E_Q R(X_p)=\sum_{r=1}^{P!} r(X_p)Q(r)$ and $Q$ is a probability mass function
on the space of all permutations of lists with $P$ elements.
The empirical counterpart is
\begin{align}
\widehat{A}_L(X_p) = \frac{1}{L-1}\sum_{i=1}^L (R_i(X_p) - \overline{R}(X_p))^2, \quad \overline{R}_L(X_p) = \frac{1}{L}\sum_{i=1}^L R_i(X_p).
\end{align}
For each item, the function $\widehat{A}_L$ has an interpretation as the expected
Euclidean distance of the individual rankings from the expected
ranking over the $L$ lists, and it corresponds to the same measure
that is used in method comparison studies to compute the limits of
agreement \citep{alt:bland:1983}.

For an integer $1\le d\le P$ we define the expected set of unique
items found by merging the first $d$ elements across the possible
lists:
\begin{align}
S(d) &= \left\{X_p; \left(\sum_{r=1}^{P!} 1\left(r(X_p)\le d\right) Q(r)\right) >0\right\}\label{eq:sumset}\\
     &= \left\{X_p; Q(R(X_p) \leq d) > 0 \right\}\nn
\end{align}
where $1(\cdot)$ denotes the indicator function.
The empirical counterpart the set of unique items ranked less than or
equal to $d$ in any of the $L$ lists:
\begin{equation}
\widehat{S}_{L}(d) = \left\{X_p; \left(\frac{1}{L}\sum_{l=1}^L 1\left(R_l(X_p)\le d\right)\right)>0\right\},
\end{equation}
which is exemplified in Panel (c) of Table \ref{tab:example}.
We then define the \emph{sequential rank agreement} as the weighted
expected agreement of the items found in the set $S(d)$:
\begin{align}
  \textrm{sra}(d) = \frac{1}{|S(d)|}\sum_{p \in S(d)}A(X_p)\label{def:sra}
\end{align}
where $|S(d)|$ is the cardinality of the set $S(d)$.
The empirical counterpart is equivalently given by
\begin{equation}
  \widehat{\textrm{sra}}_L(d) = \frac{\sum_{\{p \in \widehat{S}_{L}(d)\}}(L-1)\widehat{A_L}(X_p)}{(L-1)|\widehat {S}_{L}(d)|}.\label{def:sraEst}
\end{equation}

Values of \textrm{sra} close to zero suggests that the lists agree
while larger values suggest disagreement.
Just like in method comparison studies we prefer smaller limits of
agreement because that means that the differences between the methods
is small. If the ranked lists are identical then the value of
sequential rank agreement will be zero for all depths $d$.
The sequential rank agreement is  equivalent to the pooled
variance of the items found in $S(d)$, and it can be interpreted as the
average distance of the individual rankings of the lists from the
average ranking for each of the items we have seen until depth $d$.
For an easier interpretation we suggest to plot $\widehat{\textrm{sra}}_L(d)^{1/2}$ 
corresponding to the pooled standard deviation.

@@

With fully observed lists we can plot the sequential rank agreement
\ref{def:sra} as a function of depth $d$. An example is seen in top
panels of Figure~\ref{fig:example1} where four analysis methods were
used to rank 3051 gene expression values measured on 38 tumor mRNA
samples in order to classify between acute lymphoblastic leukemia
(ALL) and acute myeloid leukemia (AML)
\citep{Golub1999}. Preprocessing of the gene expression data was done
as described in \citet{Dudoit2002} and the four different analysis
approaches were: marginal two-sample $t$ tests, marginal logistic
regression analyses, elastic net logistic regression
\citep{friedman2010regularization}, and marginal maximum information
content correlations (MIC) \citep{Reshef2011}. For the first two
methods, the genes were ranked according to minimum $p$ value, for
logistic regression the genes were ordered by size of the
corresponding coefficients (after standardization), and MIC was
ordered by absolute correlation which resulted in the top rankings
seen in Table~\ref{tab1}.

@@

\subsection{Comparison to average overlap}
The average overlap is a measure that is widely used in comparisons of
two fully observed ranked lists \citep{Fagin2003,Webber2010} and the
idea behind the average overlap closely resembles the sequential rank
agreement. In this section we present an extension of the average
overlap to more that two lists and compare this to sequential rank
agreement.

The overlap among $L$ lists observed until depth $d$ is defined as the
proportion of items that are found in all $L$ lists compared to the
possible number of items found in all lists observed until depth $d$:
\begin{align}
  O(d) = \frac{| \cap_{l=1}^L \{R_l^{-1}(r); r\leq d \} |}{d}\label{def:overlap}
\end{align}
Typically the overlap is only considered for pairwise comparisons
\citep{Bar-Ilan2006,Boulesteix2009} but formula \ref{def:overlap}
is easily extended to the situation where $L>2$ as shown above.

\section{Evaluating sequential rank agreement}
To interpret the sequential rank agreement values we propose two
different benchmark values corresponding to two different
hypotheses. We wish to determine if we observe better agreement than
what would be expected if there were no relevant information available
in the data.

@@

\section{Asymptotics}\label{sec:chgpoint}
In many applications it is of interest to estimate a list depths which
satisfies a change point criterion. In this section we investigate the
theoretical properties of our proposed method for this specific
task. As Hall and Schimek \mcomment{REF}, we work with an infinite set of lists
and study the asymptotic behaviour for $L\to\infty$.
However, we do not allow the length of the lists to
change with $L$ as in most applications the length of the lists is fixed.

First, we define the parameter of interest. For any given threshold value $q$, 
a change-point $d^\ast(q)$ in the list agreement is defined by
\begin{equation}
  d^\ast(q) = \argmin_{d\in\{1,\dots,P\}}\textrm{sra}(d)>q.
\end{equation}
The value of $q$ could for example be the agreement of randomly
permuted lists. The corresponding estimated change-point is similarly defined by
\begin{equation}
\widehat{d^\ast_L}(q) = \argmin_{d\in\{1,\dots,P\}}\widehat{\textrm{sra}}_L(d)>q
\end{equation}

We start by showing that $\widehat{\textrm{sra}}_L$ is a consistent estimator of $\textrm{sra}$ for $L \rightarrow \infty$.
The consistency of $\widehat{d^\ast_L}(q)$ then follows by a simple corollary. The proof requires the following assumptions.

\begin{assumption}
We assume that:
\begin{enumerate}[label=\Alph*)]
\item{$\E_Q[R(X_p)^4]$ is finite for all $p \in 1,\ldots,P$}.
\item{$|S(d)| > 0$ uniformly in $d$}.
\end{enumerate}
\end{assumption}
We note that assumption $B$ implies that for every list depth $d$ there must be a non-zero probability of ... under the probability measure $Q$.

\begin{theorem}
Under the assumptions it follows that $\left\|\widehat{\textrm{sra}}_L - \textrm{sra}\right\|_\infty = o_P(1)$.
\label{thm:consistency}
\end{theorem}

\begin{corollary}
For fixed $q$ it follows from Theorem \ref{thm:consistency} that
$\widehat{d^\ast_L}(q) \overset{P}{\longrightarrow} d^\ast(q)$
for $L \rightarrow \infty$.
\label{cor:consistency}
\end{corollary}

@@

\appendix

\newpage
\section{Proof of Theorem \ref{thm:consistency}}
We start by defining the following cadlag function
\begin{align}
  N(p; d) = \sum_{s=1}^p 1\left(Q(R(X_s) \leq d) > 0\right), \quad p = 1,\ldots, P
\end{align}
which jumps at a time $p$ if the probability that the rank of $X_p$ is less than or equal to $d$ is bounded away from zero under the probability measure $Q$.
Similarly we have the empirical counterpart
\begin{align}
  \widehat{N}_L(p; d) &= \sum_{s=1}^p 1\left( \frac{1}{L} \sum_{l=1}^L 1(R_l(X_s) \leq d) > 0\right)\\
        &= \sum_{s=1}^p 1\left(\widehat{Q}_L(R(X_s) \leq d) > 0\right)\nn
\end{align}
Since the joint distribution of $\left\{\widehat{N}_L(p;d) : p=1,\ldots,P\right\}$ is completely determined by its finite set of jump times and $\widehat{Q}_L(R(X_p) \leq d) \overset{P}{\longrightarrow} Q(R(X_p) \leq d)$ for every $p$ and $d$ for $L \rightarrow \infty$ by the law of large numbers, it follows that
\begin{align}
  \sup_{d \in 1,\ldots,P}\sup_{p \in 1,\ldots, P} \left|\widehat{N}_L(p; d) - N(p; d)\right| = o_P(1)\label{eq:countingConv}
\end{align}

Recalling the definition of the sequential rank agreement in equation (\ref{def:sra}), it may be rewritten as the following integral with respect to the counting measure induced by $N$
\begin{align}
  \textrm{sra}(d) = \int_{1}^P \frac{A(X_p)}{N(P; d)}dN(p; d)
\end{align}
where we note that the cardinality of the set $S(d)$ in equation (\ref{eq:sumset}) is equal to the counting process evaluated at $P$.
The empirical sequential rank agreement is similarly given by
\begin{align}
  \widehat{\textrm{sra}}_L(d) &= \int_1^P \frac{\widehat{A_L}(X_p)}{\widehat{N}_L(P; d)}d\widehat{N}_L(p; d) 
\end{align}
and by elementary algebra it follows that
\begin{align}
  \sup_{d \in 1,\ldots,P}\left|\widehat{\textrm{sra}}_L(d) - \textrm{sra}(d)\right| \leq \sup_{d \in 1,\ldots,P}\left|U_L(d)\right| - \sup_{d \in 1,\ldots,P}\left|V_L(d)\right|
\end{align}
where
\begin{align}
  U_L(d) &= \int_1^P\frac{A(X_p)}{N(P;d)} d\left(\widehat{N}_L(p; d) - N(p; d)\right)\\
  V_L(d) &=  \int_1^P \left(\frac{\widehat{A_L}(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right)d\widehat{N}_L(p; d)
\end{align}
The conclusion of the proof therefore follows if each of these two terms are uniformly of order $o_P(1)$ in $d$.

Starting with $V_L(d)$, since $\widehat{N}_L$ is of bounded variation it follows that
\begin{align}
 V_L(d) &\leq \sup_{p \in 1,\ldots,P}\left|\frac{\widehat{A_L}(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right| \int_1^P \left|d\widehat{N}_L(p; d)\right|\label{eq:secondTerm}
\end{align}
Looking at $\widehat{A_L}(X_p)$ we have that
\begin{align}
  ??
\end{align}
Therefore, under assumption A) we have that ... and therefore $\widehat{A_L}(X_p) = A(X_p) + o_P(1)$ uniformly in $p$. A consequence of equation (\ref{eq:countingConv}) is that $\widehat{N}_L(P; d) = N(P;d) + o_P(1)$ uniformly in $d$ and therefore by the continuous mapping theorem and assumption B) the first factor in equation (\ref{eq:secondTerm}) is of order $o_P(1)$ uniformly in $p$ and $d$. The result then follows by noting that the second factor is bounded by $P$ uniformly in $d$.

Continuing with $U_l(d)$ we have that
\begin{align}
	...
\end{align}
using integration by parts.

\begin{align}
S_d &= \left\{X_p; \left(\sum_{r=1}^{P!} I\{r(X_p)\le d\} Q(r)\right) >0\right\}\\
    &= \left\{X_p; \E[I\{R(X_p)\le d\}] >0\right\}\\
    &= \left\{X_p; P(R(X_p)\le d) > 0\right\}\\
\widehat{S}_{d,L} &= \left\{X_p; \left(\sum_{l=1}^L I\{R_l(X_p)\le d\}\right)>0\right\}
\end{align}
This completes the proof.

\section{Proof of corollary \ref{cor:consistency}}
